Including EW and mixed QCD-EW corrections into PDF fits

### 2020-06-12 paper/sec-doublecounting.tex
added few refs

A common source of inconsistency is the subtraction of (irreducible) background processes which must not be considered as such. The typical example
is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
at $\mathcal O(\alpha^2)$. Because this process is usually thought
as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
corrections. For example, in Ref.~\cite{Aaboud:2017ffb}, one reads:
\begin{quote}
The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
\end{quote}
Such a distinction cannot be physically
justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
includes both kind of topologies. {\bf MZ add Feynman diags}

>>>>

A common source of inconsistency is the subtraction of (irreducible) background processes which must not be considered as such. The typical example
is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
at $\mathcal O(\alpha^2)$. Because this process is usually thought
as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, and it 
subtracted, possibly evaluated with different parton densities and/or including (unphysical) higher-order 
corrections. For example, in Refs.~\cite{Aaboud:2017ffb,Aad:2016zzw}, one reads:
\begin{quote}
The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
\end{quote}
A similar statement appears also in an older analysis~\cite{Aad:2013iua}. Such a distinction cannot be physically
justified beyond LO\@. Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
includes both kind of topologies. {\bf MZ add Feynman diags}
